\textbf{ Interpretable Gaussian Processes for Stellar Variability\\ I: Static Surfaces }

### 2020-12-22 tex/ms.tex
chugging along

\xxx{TODO: discuss the batch calibration default run.}

@@

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble.pdf}
        \\
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble_ld.pdf}
        \\
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble_ld_var.pdf}
        \oscaption{nullspace_ensemble}{%
            \emph{Top:} Posterior shrinkage as a function of spherical harmonic degree
            for a hypothetical scenario in which an observer can measure a
            stellar light curve at 1 (blue),
            3 (orange), 10 (green), and 30 (red)
            random inclinations. The thicker curves correspond to
            the mean shrinkage for each experiment.
            The information content in the light curve of a star observed
            from a single vantage point approaches zero as $l$
            increases. However, observing the star from many vantage points
            allows one to recover nearly all of the information in the
            even spherical harmonic modes. This is why ensemble analyses of
            many similar stars at different inclinations allows us to infer
            their surface properties.
            \emph{Middle:} Same as the top panel, but for limb-darkened
            stars with coefficients $u_1 = 0.5$ and $u_2 = 0.25$. Odd
            modes can now be probed, at the expense of the even modes.
            \emph{Bottom:} Same as the middle panel, but allowing for
            a 10\% variation in each of the two limb darkening coefficients
            across different observations. For ${\gtrsim}30$ light curves,
            there is virtually no null space up to $l_\mathrm{max} = 15$.
            \label{fig:nullspace_ensemble}
        }
    \end{centering}
\end{figure}

>>>>

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.85\linewidth]{figures/calibration_batch_default_corner.pdf}
        \oscaption{calibration_batch_default}{%
            Similar to Figure~\ref{fig:calibration_default_corner}, but
            showing the posterior distribution for 100 different synthetic
            datasets, all generated from the same default input parameters
            (Table~\ref{tab:synthetic}). Each colored histogram corresponds to a single
            run, with the corresponding $1\sigma$ contours shown as shaded ellipses for each pair
            of parameters. The black histograms correspond to the distributions of all
            samples from each of the 100 runs, and the black curves again indicate
            $1\sigma$ contours in the joint posterior.
            \label{fig:calibration_batch_default_corner}
        }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.5\linewidth]{figures/calibration_batch_default_inclinations.pdf}
        \oscaption{calibration_batch_default}{%
            Distribution of stellar inclination residuals normalized to the posterior
            standard deviation for all $5{,}000$ stars across the 100 trials in
            Figure~\ref{fig:calibration_batch_default_corner} (blue). The
            standard normal distribution is shown in orange for comparison.
            The inclination posteriors inferred with our GP are largely unbiased and
            have the expected variance.
            \label{fig:calibration_batch_default_inclinations}
        }
    \end{centering}
\end{figure}

\xxx{TODO: discuss the batch calibration default run.}
Stellar inclination residuals (posterior mean minus true value) normalized to the
posterior standard deviation. Only \emph{marginally} overestimate the variance.

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/calibration_equatorial_corner.pdf}
        \\[1em]
        \includegraphics[width=\linewidth]{figures/calibration_equatorial_latitude.pdf}
        \oscaption{calibration_equatorial}{%
            Same as Figure~\ref{fig:calibration_midlat}, but for
            equatorial spots with $\mu_\phi = 0^\circ$.
            \label{fig:calibration_equatorial}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble.pdf}
        \\
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble_ld.pdf}
        \\
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble_ld_var.pdf}
        \oscaption{nullspace_ensemble}{%
            \emph{Top:} Posterior shrinkage as a function of spherical harmonic degree
            for a hypothetical scenario in which an observer can measure a
            stellar light curve at 1 (blue),
            3 (orange), 10 (green), and 30 (red)
            random inclinations. The thicker curves correspond to
            the mean shrinkage for each experiment.
            The information content in the light curve of a star observed
            from a single vantage point approaches zero as $l$
            increases. However, observing the star from many vantage points
            allows one to recover nearly all of the information in the
            even spherical harmonic modes. This is why ensemble analyses of
            many similar stars at different inclinations allows us to infer
            their surface properties.
            \emph{Middle:} Same as the top panel, but for limb-darkened
            stars with coefficients $u_1 = 0.5$ and $u_2 = 0.25$. Odd
            modes can now be probed, at the expense of the even modes.
            \emph{Bottom:} Same as the middle panel, but allowing for
            a 10\% variation in $u_1$ and $u_2$
            across different observations. For ${\gtrsim}30$ light curves,
            there is virtually no null space up to $l_\mathrm{max} = 15$.
            \codelink{nullspace_ensemble_ld}
            \codelink{nullspace_ensemble_ld_var}
            \label{fig:nullspace_ensemble}
        }
    \end{centering}
\end{figure}
